    ---
title: "README Assignment B2"
author: "Andrea_Ku"
date: "11/16/2021"
output: github_document
---

## R Package Description: 
#### This package runs summary statistics with dplyr on data from the datateachr package. Summary statistics include minimum, maximum, and mean.

## Installation Instructions:
#### Install this package by loading the following package dependencies:

```{r}
# install.packages("devtools")
devtools::install_github("AndreaKu/Stat545BAndreaKu")
```

## Usage is demonstrated with data from the datateachr package: 
#### Examples are included for the Flow_samples, Vancouver_trees, and Cancer sample datasets.

```{r}
library(function1)

#' @example
#' 1. An example of the function ran in Flow_Samples dataset
#'
#' @description  Flow Summary statistics from MDA:

Function1(datateachr::flow_sample,month,flow)

#' @example
#' 2. An example of the function ran in Vancouver_Trees dataset
#'
#' @description Calculates summary statistics for each genus name.

Function1(datateachr::vancouver_trees,genus_name,diameter)

#' @example
#' 3. An example of the function ran in Cancer_Sample dataset
#'
#' @description Calculates summary statistics for each diagnosis type.

Function1(datateachr::cancer_sample,diagnosis,radius_mean)

